---
title: "lesson3"
output: html_document
---

### Create a histogram of the price of all the diamonds
```{r}
ggplot(aes(x=price), data=diamonds) +
  geom_histogram(binwidth = 1, color="black", fill="#f79420") +
  scale_x_sqrt(limits=c(350,18500), breaks=seq(300,18500,1000)) + 
  #scale_y_log10() +
  ylab("Amount of diamonds") +
  xlab("Price") +
  facet_wrap(~cut, ncol=5, scales = "free_y")
summary(df$price)

```
##Histogram price per carat
```{r}
liggplot(aes(x=price/carat), data = df) + 
  geom_histogram(binwidth = 0.05, color="black", fill="#f79420") + 
  scale_x_log10() +
  ylab("Count") +
  xlab("Price per carat") +
  facet_wrap(~cut, ncol = 5, scales = "free_y")
ggsave("Price per carat.png")

```
##Boxplots price depending on clarity and color
```{r}
p1<- ggplot(aes(y = price, x = clarity), data=df) + 
  geom_boxplot(outlier.colour = "red", colour="black", fill="#09dd99") + 
  coord_cartesian(ylim=c(0,7000)) +
  ylab("Price") +
  xlab("Clarity")

p2<- ggplot(aes(x=color, y = price), data = df) + 
  geom_boxplot(outlier.colour = "red", fill="#099dd9") + 
  coord_cartesian(ylim=c(0,8000)) +
  ylab("Price") + 
  xlab("Color")

grid.arrange(p1,p2, nrow=2)
ggsave("boxplots color and clarity.png",plot = grid.arrange(p1,p2,nrow=2))

by(df$price, df$clarity, summary)
by(df$price, df$color, summary)

```
##Boxplot price per carat across color
```{r}
ggplot(aes(x=color, y = price/carat), data = df) + 
  geom_boxplot(outlier.colour = "red", fill="#099dd9") + 
  coord_cartesian(ylim=c(0,7500)) +
  ylab("Price per Carat") + 
  xlab("Color")

#ggsave("boxplots price per carat across colors.png")
```
##Frequency polygon diamonds
```{r}
ggplot(aes(x=carat), data= df) + 
  geom_freqpoly(aes(color=carat), binwidth=.1) +
  scale_y_continuous(breaks=seq(500,11500,1000)) +
  scale_x_continuous(breaks=seq(0,6.1,0.1))

```


##Histogram of users' birthdays
```{r}
library(ggplot2)

names(pf)
ggplot(aes(x=dob_day), data = pf) +
    geom_histogram(binwidth = 1) +
    scale_x_continuous(breaks=1:31) +
    facet_wrap(~dob_month, ncol = 3)
```

##Histogram of friend count
```{r}
ggplot(aes(x=friend_count), data = subset(pf, !is.na(gender))) +
    geom_histogram(binwidth = 10) +
    scale_x_continuous(limits = c(0,1000), breaks= seq(0,1000,50)) +
    facet_wrap(~gender)
    
```

##Statistics by 'Gender'
```{r}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

##Histogram of tenure
```{r}
ggplot(aes(x=tenure/365), data=pf) +
    xlab('Number of years using Facebook') +
    ylab('Number of users in sample') +
    geom_histogram(binwidth = .25, color = 'black', fill='#f79420') +
    scale_x_continuous(breaks=seq(1,7,1), limits=c(0,7))
```

##Histogram of age
```{r}
#old.par <- par(mfrow=c(2,2), pty = 's')
p1<-ggplot(aes(x=age), data=pf) +
    xlab('Age of Facebook Users') +
    ylab('Number of users in sample') +
    geom_histogram(binwidth = 1, color='black', fill='#099dd9') +
    scale_x_continuous(limits = c(15,85), breaks=seq(15,85,5))

p2<-ggplot(aes(x=age), data=subset(pf, !is.na(gender))) +
    xlab('Age of Facebook users') +
    ylab('Number of users in sample') + 
    geom_histogram(binwidth = 1,color='black', fill='#f79420') +
    scale_x_continuous(limits = c(15,85), breaks=seq(15,85, 5)) +
    #scale_y_log10() +
    facet_wrap(~gender)

grid.arrange(p1,p2, ncol=1)    
```

##Friend count log- and sqrt-transformed
```{r}
org<- ggplot(aes(x = friend_count), data = pf) +
  xlab("Number of Facebook friends") +
  ylab("Number of users in sample") +
  geom_histogram(binwidth = 50, color="black", fill="#099dd9") +
  scale_x_continuous(limits= c(0,1000), breaks=seq(0,1000,50))

log_trans <- ggplot(aes(x=(friend_count+1)), data = pf) +
  xlab("Number of Facbook friends") +
  ylab("Number of users in sample") +
  geom_histogram(binwidth = 0.1, color = "black", fill = "#f79420") +
  scale_x_log10()

sqrt_trans <- ggplot(aes(x=friend_count), data = pf) +
  ylab("Number of users in sample") +
  xlab("Number of Facebook friends") + 
  geom_histogram(binwidth = .25, color = "black", fill = "#008b45")+
  scale_x_sqrt(limits=c(0,1000), breaks=seq(0,1000,50))
  
grid.arrange(org, log_trans, sqrt_trans, ncol=1)
```

##Frequency polygon friend_count/gender
```{r}
ggplot(aes(x = friend_count),data= subset(pf, !is.na(gender))) +
  geom_histogram(binwidth = 20, fill = "#099dd9") +
  scale_y_log10() +
  scale_x_continuous(limits = c(500,2500), breaks= seq(500,2500,50))

ggplot(aes(x = friend_count, y=..count../sum(..count..)),data= subset(pf, !is.na(gender))) +
  geom_freqpoly(binwidth = 20, aes(color=gender)) +
  scale_x_continuous(limits = c(500,2500), breaks= seq(500,2500,50)) +
  xlab("Friend count") +
  ylab("Numbers of users with that friend count")

```
##Frequency polygon gender/number of likes
```{r}
pf <- read.csv("pseudo_fb.tsv", sep = "\t")
ggplot(aes(x=www_likes, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color=gender), binwidth = .15) +
  scale_x_log10(breaks=c(0,10,50,100,500, 1000,2000,5000,10000,15000, 22500))+
  #scale_x_continuous(limits = c(0,15000), breaks=seq(0,15000,250)) +

  #scale_y_log10() +
  ylab("Proportion of users with that amount of likes") + 
  xlab("Number of likes")


```
##Boxplot gender/number of www likes
```{r}
ggplot(aes(x=gender, y=friend_count), data = subset(pf,!is.na(gender))) + 
  geom_boxplot() + 
  coord_cartesian(ylim=c(0,250)) +
  ylab("Number of friends") +
  xlab("Gender")

```

```{r}
ggplot(aes(x=gender, y=friendships_initiated), data=subset(pf,!is.na(gender))) + 
  geom_boxplot() +
  coord_cartesian(ylim=c(0,250)) +
  ylab("Number of friendships initiated") +
  xlab("Gender")

by(pf$friendships_initiated, pf$gender, sum)
by(pf$friendships_initiated, pf$gender, summary)
```


```{r}
mobile_check_in <- NA
mobile_check_in <- ifelse(pf$mobile_likes > 0, 1,0)

length(mobile_check_in[mobile_check_in>0])/length(mobile_check_in)


```

