Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:
qplot(x = age, y = friend_count, data = df)
```{r Scatterplots}
ggplot(aes(x=age, y=friend_count), data = df) + geom_point() + xlim(13,90)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age, y=friend_count), data = df) + geom_point(alpha = 1/20, position = position_jitter(h = 0)) + xlim(13,90) + coord_trans(y="sqrt") + geom_line(stat="summary", fun.y=mean)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

p1<-ggplot(aes(x=age, y=friendships_initiated, colour=friendships_initiated), data = df) + geom_point(alpha = 1/20, position = position_jitter(h=0)) + xlim(c(15,90)) + coord_trans(y="sqrt") + scale_colour_gradientn(colours=terrain.colors(15)) + ylab("Friendships initiated") + xlab("Age of Facebook User") + ggtitle("Number of friendships initiated\ndepending on the age")

p2 <- ggplot(aes(x=age, y=friendships_initiated, colour=friendships_initiated), data = subset(df,!is.na(gender))) + geom_point(alpha = 1/20, position = position_jitter(h=0)) + xlim(c(15,90)) + coord_trans(y="sqrt") + scale_colour_gradientn(colours=rainbow(15)) + ylab("Friendships initiated") + xlab("Age of Facebook User") + ggtitle("Number of friendships initiated\ndepending on the age and gender") + facet_wrap(~gender)

grid.arrange(p1,p2, nrow=2)
ggsave('friendship.png')
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
age_groups <- group_by(df, age)
df.fc_by_age <- summarise(age_groups, 
          friend_count_mean = mean(friend_count), 
          friend_count_median = median(friend_count),
          n = n())
df.fc_by_age <- arrange(df.fc_by_age, age)
tbl_df(df.fc_by_age)
df.fc_by_age
```
Alternatively:
```{r}
df.fc_by_age <- df %>% 
  group_by(age) %>%
  summarise(
    friend_count_mean = mean(friend_count), 
          friend_count_median = median(friend_count),
          n = n()
  ) %>%
  arrange(age)
tbl_df(df.fc_by_age)
df.fc_by_age

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x=age, y=friend_count_mean, colour=friend_count_mean), data=df.fc_by_age) + geom_line() + scale_fill_gradientn(colours = terrain.colors(10)) + coord_trans(y="sqrt") + xlim(13,90) + ylim(70,410) + ylab("Mean of number of friends") + xlab("Age of Facebook user") + ggtitle("Mean of number of friends given\nfor the respective age")
ggsave("CondMeans.png")
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x=age, y=friend_count, colour=friend_count), data = df) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) + 
  coord_trans(y="sqrt") +
  coord_cartesian(xlim = c(13,50), ylim=c(0,1000)) + 
  geom_line(stat="summary", fun.y=mean) +
  geom_line(stat="summary", fun.y=quantile, fun.args=list(probs=.1), color="red", linetype=2) +
  geom_line(stat = "summary", fun.y=quantile, fun.args=list(probs=.9), color="red", linetype=2) +
  geom_line(stat = "summary", fun.y=median, linetype=1, colour = "red")
  scale_color_gradientn(colours = rainbow(1))
  
ggsave("means_and_quantile.png")
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
with(df, cor.test(friend_count,age, method="pearson"))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(df,age<=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(y=likes_received, x=www_likes_received, colour=likes_received), data = df) +
    geom_jitter(alpha=1/20,position = position_jitter(h=0)) +
    geom_smooth(formula = y~x,method = "lm", fill="yellow", colour="lightgreen") +
    xlim(0, quantile(df$www_likes_received,0.95))+
    ylim(0,quantile(df$likes_received,.95))+
    #coord_trans(x="log10", y="log10")+
    #geom_line(stat = "summary", fun.y = median, color = "red") +

    ylab("Number of likes received") + 
    xlab("Number of likes received from desktop version")
ggsave("likesReceived2.png")
cor.test(df$www_likes_received, df$likes_received)
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x=Month, y=Temp), data = Mitchell) + 
  geom_point() +
  scale_x_continuous(breaks=seq(0,203,12))
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
0.05
b. What is the actual correlation of the two variables?
(Round to the thousandths place)
0.05747063
```{r Noisy Scatterplots}
ggplot(aes(x=Month%%12, y=Temp), data = Mitchell) + 
  geom_point() #+
  #scale_x_continuous(breaks=seq(0,203,12))
```

***

### Making Sense of Data
Notes:
There are other measures of associations that can detect this. The dcor.ttest() function in the energy package implements a non-parametric test of the independence of two variables. 
```{r Making Sense of Data}
x <- seq(0, 4*pi, pi/20)
y <- cos(x)
qplot(x,y)
dcor.ttest(x,y)
cor.test(x,y)
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
age_and_month <- df[,c(2,5)]
age_with_month <- age_and_month[,1] + (12 - age_and_month[,2])/12
backup <- df
df$age_with_months <- age_with_month
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months <- df %>% group_by(age_with_months) %>% 
  summarise(friend_count_mean = mean(friend_count), friend_count_median = median(friend_count), n=n())
pf.fc_by_age_months <- arrange(pf.fc_by_age)
pf.fc_by_age_months
```

Programming Assignment
```{r Programming Assignment}
ggplot(aes(y=friend_count_mean, x=age_with_months), data=subset(pf.fc_by_age_months, age_with_months <71)) + geom_line()
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
p1 <- ggplot(aes(y=friend_count_mean, x=age_with_months), data=subset(pf.fc_by_age_months, age_with_months <71)) + geom_line() +
  geom_smooth()

p3 <- ggplot(aes(y=friend_count_mean, x=age), data=subset(df.fc_by_age, age <71)) + geom_line() +
  geom_smooth()

p2 <- ggplot(aes(y=friend_count, x=round(age/5)*5), data=subset(df, age <71)) + geom_line(stat="summary", fun.y=mean)



grid.arrange(p1,p2,p3,ncol=1)

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

