Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

```{r}
ggplot(aes(x = gender, y = age), data = subset(pf, !is.na(gender))) +
  geom_boxplot() + stat_summary(fun.y = mean, geom="point", shape=4)

ggplot(aes(x=age, y=friend_count), data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color=gender), stat="summary", fun.y=median) + scale_color_discrete(name="Gender")

```


***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable, echo=FALSE}
pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>% 
  group_by(age,gender) %>%
  summarise(mean_friend_count = mean(friend_count, na.rm=T), 
            median_friend_count = trunc(median(friend_count, na.rm=T)), 
            n = n()) %>% 
  ungroup() %>% 
  arrange()
head(pf.fc_by_age_gender)
tail(pf.fc_by_age_gender)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x=age, y=median_friend_count), data = pf.fc_by_age_gender) + 
  geom_line(aes(colour = gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
library(reshape2)
pf.fc_by_age_gender.wide <- tbl_df(dcast(pf.fc_by_age_gender, age ~ gender, value.var = "median_friend_count"))
pf.fc_by_age_gender.wide2 <- spread(pf.fc_by_age_gender[,c("age", "gender", "median_friend_count")], gender, median_friend_count)
head(pf.fc_by_age_gender.wide)
head(pf.fc_by_age_gender.wide2)
identical(pf.fc_by_age_gender.wide2,pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
pf.fc_by_age_gender.wide <- mutate(pf.fc_by_age_gender.wide, ratio = female/male)
p1 <- ggplot(data=pf.fc_by_age_gender.wide, aes(x=age, y=female/male)) + 
  geom_line(color='#f79420', show.legend = F) + 
  geom_hline(yintercept = 1, linetype=2) + 
  ylab("Female to male ratio") + 
  xlab("Age") + 
  #scale_color_discrete(name="Female to male ratio", breaks="female/male") + 
  ggtitle("Female to male ratio regarding number of Facebook friends\ndepending on the user's age")

p2 <- ggplot(aes(x=age, y =ratio), data=pf.fc_by_age_gender.wide) + 
  geom_line(color="#099dd9", show.legend = F) + 
  geom_hline(yintercept = 1, linetype=2) + 
  ylab("Female to male ratio") + 
  xlab("Age") +
  #scale_color_discrete(name="Female to male ratio") + 
  ggtitle("Female to male ratio regarding number of Facebook friends\ndepending on the user's age")

grid.arrange(p1,p2, ncol=1)

ggsave("female to male facebook friends ratio.png")

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}

```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}

```

***

### Friending Rate
Notes:

```{r Friending Rate}

```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

